Dashboard section

### 2022-08-02 Report/Old/Draft Dashboard section.Rmd
Cleaning.

Flexdashboard and Shiny do not fail particularly gracefully, so in addition to the information to the user and the information about file types provided to the browser, the Shiny logic executed on the button press includes some basic validations using `validate()` and `tools::file_ext()` which output error messages if the wrong file has been uploaded. (Note that the `accept` argument is not obeyed by the RStudio viewer, but most ordinary browsers enforce the instruction)

@@

If the validation is successful the files are read using the functions developed for this purpose, which conduct further testing, outputting error messages using `validate()`:
```{r dashboard_file_functions, eval=FALSE, class.source = "fold-hide"}
# Data reading functions =======================================================

### Second Excel function - creating primary Excel data frame-------------------
widen_excel <- function(object) {
  # testing if all columns are present
  if (setequal(
    names(object),
    c("year", "firm", "category", "sub_category", "name", "value")
  )) {
    object |>
      # uniting category and name to deal with multiple 'Other'
      unite(
        entry, c(category, name)
      ) |>
      # deleting Sub-category and Firm
      select(-sub_category, -firm) |>
      # pivoting to create 'tidy' variables
      pivot_wider(names_from = entry, values_from = value) |>
      # cleaning names
      clean_names()
    # Notification if all columns are not present
  } else {
    validate("Please upload data using the specified Excel template.")
  }
}
```

Using these functions, the actual creation of data frames takes place in two stages for each file, partially for data testing and partially to create subsidiary data frames used by some functions:
```{r dashboard_data_frames, eval=FALSE}
# Data frames ================================================================
## Creating data frame from html file-----------------------------------------
html_currency <- reactive({
  # validating file
  validate(need(
    tools::file_ext(input$html$datapath) == "html",
    "Please upload an html file."
  ))

@@

The file name of the report is created by combining the name of the NGO from the `title()` reactive and the output of `Sys.Date()`, furnishing a hopefully informative file name. (Note that this only works when the dashboard is run in an ordinary browser and not in the RStudio viewer.)

<!--# Parenthesis as footnote? -->
```{r}
# Report Output ==============================================================

@@

>>>>

Flexdashboard and Shiny do not fail particularly gracefully, so in addition to the information to the user and the information about file types provided to the browser, the Shiny logic executed on the button press includes some basic validations using `validate()` and `tools::file_ext()` which output error messages if the wrong file has been uploaded.^[Note that the `accept` argument is not obeyed by the RStudio viewer, but most ordinary browsers enforce the instruction.]

@@

If the validation is successful the files are read using the functions developed for this purpose, which conduct further testing, outputting error messages using `validate()`. Using these functions, the actual creation of data frames takes place in two stages for each file, partially for data testing and partially to create subsidiary data frames used by some functions.^[The data reading code is included as an appendix because of its length.]

@@

The file name of the report is created by combining the name of the NGO from the `title()` reactive and the output of `Sys.Date()`, furnishing a hopefully informative file name.^[Note that this only works when the dashboard is run in an ordinary browser and not in the RStudio viewer.]

```{r}
# Report Output ==============================================================

@@

# Appendix: Data reading and cleaning code
```{r dashboard_file_functions, eval=FALSE}
# Data reading functions =======================================================

### Second Excel function - creating primary Excel data frame-------------------
widen_excel <- function(object) {
  # testing if all columns are present
  if (setequal(
    names(object),
    c("year", "firm", "category", "sub_category", "name", "value")
  )) {
    object |>
      # uniting category and name to deal with multiple 'Other'
      unite(
        entry, c(category, name)
      ) |>
      # deleting Sub-category and Firm
      select(-sub_category, -firm) |>
      # pivoting to create 'tidy' variables
      pivot_wider(names_from = entry, values_from = value) |>
      # cleaning names
      clean_names()
    # Notification if all columns are not present
  } else {
    validate("Please upload data using the specified Excel template.")
  }
}

# Data frames ================================================================
## Creating data frame from html file-----------------------------------------
html_currency <- reactive({
  # validating file
  validate(need(
    tools::file_ext(input$html$datapath) == "html",
    "Please upload an html file."
  ))
